
```{r}
library(caret)
library(rpart)
library(rpart.plot)

```

###Loading Data
```{r}

testing_data  <-read.csv("~/Desktop/pml-testing.csv")
training_data <-read.csv("~/Desktop/pml-training.csv")
```

###Seperating  Data
```{r}
inTrain <- createDataPartition(training_data$classe,p=0.75,list=F)
train_1 <- training_data[inTrain,]
train_2  <-training_data[-inTrain,]
```

###Cleaning Up the Data 
In this section I will try  to remove those variables which i feel will not have any significant impact on the outcome of our project ;Sice most of the not needed variables possess lot of missing values ,thus making then unusable.

```{r}
Not_required <- nearZeroVar(train_1)
training_1 <-train_1[,-Not_required]
training_2 <-train_2[,-Not_required]
NA_values <- sapply(training_1,function(x) mean(is.na(x))) >0.95
ptrain1 <- training_1[, NA_values==FALSE]
ptrain2 <- training_2[, NA_values==FALSE]
ptrain1 <- ptrain1[, -(1:5)]
ptrain2 <- ptrain2[, -(1:5)]

```

###Fitting a Model and Using Cross Validation 

####Fitting a Classification Tree 
```{r,eval=FALSE}
set.seed(2345)
model_fit <- train(classe~., data = ptrain1, method = "rpart")
predictrp <- predict(model_fit, newdata = ptrain2)
confusionMatrix(predictrp, ptrain2$classe)
fancyRpartPlot(modelrp$finalModel)

```

Using rpart the model gave poor accuracy results and is dismissed.The accuracy was found to be just 49%.

####Fitting a Random Forest Model 
```{r}

fitControl <- trainControl(method="cv", number=3, verboseIter=F)
fit <- train(classe ~ ., data=ptrain1, method="rf", trControl=fitControl)
```

```{r}
preds <- predict(fit, newdata=ptrain2)
confusionMatrix(ptrain2$classe,preds)
```

After testing the model on the test data set;The model accuracy was found to be around 99%.Thus we will use a regression tree for analysis of the 


##Predictions on  20 test cases
```{r}
prediction <- predict(fit,newdata = testing_data)
prediction
```

##Conclusions 
In this assignment i fitted the data with classification tree and random forest ,and as expected the accuracy of the random forest model was much higher then a regular classification tree.The difference in accurancy in the model was found to be as high as 48%.But keeping in mind the time it takes to load the page i decided to finally load only random forest model which was giving me the most accurate result .

